---
title: "Fall 2017 DA5020 Homework6"
author: "Xing Yang"
date: "2017/10/10"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Quesion 1

```{r}
library(tidyverse)
edu <- read_csv("/Users/xingyang/Desktop/5020/FipsEducations.csv")
unemply <- read.csv("/Users/xingyang/Desktop/5020/FipsUnemployment.csv")
head(edu)
#"county_state" contain more than one atomic value.
#Every year have four same "percent_measure" 
#Same state has same "rural_urban_cont_code" and "description" 
edusp <- spread(edu, percent_measure, percent)
head(edusp)
eduspse <- separate(edusp, county_state, into = c("state", "county"), sep = "\\|")
head(eduspse)
```

###Question 2

```{r}
fips <- eduspse %>%
  count(fips, county, state, rural_urban_cont_code)

n <- ncol(eduspse)
colnames(eduspse)[n] <- "percent_less_than_hs_diploma"
education <- eduspse %>%
  count(fips, state, county, percent_four_plus_years_college, percent_has_some_college, percent_hs_diploma, percent_less_than_hs_diploma)

rural_urban_code <-  eduspse %>%
  count(rural_urban_cont_code, description)
```

###Question 3

The fips column in the education table is it a foreign key.
The primary key for my education is the county
The primary key for the rural_urban code_table is rural_urban_cont_code.

###Question 4

```{r}
#4.0
#In 1970, the  the percent of the population not attaining a high school diploma for the Nantucket county in Massachusetts
eduspse %>%
  filter(year == 1970, county == " Nantucket County") %>%
  select(percent_less_than_hs_diploma)

#In 2015
eduspse %>%
  filter(year == 2015, county == " Nantucket County") %>%
  select(percent_less_than_hs_diploma)

#4.1
pro41 <- eduspse %>%
  filter(year == 2015, state == "AL ") %>%
  select(percent_less_than_hs_diploma)
colMeans(pro41)

#4.2
pro42 <- eduspse %>%
  filter(year == 2015, state == "MA ") %>%
  select(percent_four_plus_years_college)
colMeans(pro42)

#4.3
pro43 <- eduspse %>%
  group_by(year) %>%
  filter(state == "AL ") %>%
  summarise(
     average = mean(percent_less_than_hs_diploma)
    )
pro43 

#4.4
names(which.max(table(eduspse$rural_urban_cont_code)))

#4.5
pro45 <- eduspse %>%
  filter(rural_urban_cont_code == "NULL") %>%
  count(state, county)
pro45 <- pro45[order(pro45$state),]
pro45

#4.6
pro46 <- eduspse %>%
  filter(state == "MS ", year == 2010) %>% 
  select(percent_four_plus_years_college)
pro46

#4.7
min(pro45$n)
max(pro45$n)

#Since the maximum value is equal the minimum value, not providing a rural code for  each conuty has the same "NULL" number with 5. So there is no the most number of counties.

#4.8
all = full_join(eduspse, unemply)
pro48 <- all %>%
  filter(percent_unemployed > percent_four_plus_years_college) %>%
   select(county, state)
pro48 <- pro48[order(pro48$state),]
pro48

#4.9
pro49 <- eduspse %>%
  arrange(percent_four_plus_years_college) %>%
  select(county, state, year)
pro49[nrow(pro49),]
```

###Question 5

```{r}
#common period 2015
q5 <- all %>%
  filter(year == 2015) %>%
  select(state, county, percent_less_than_hs_diploma, percent_unemployed)

ggplot(q5, mapping = aes(percent_less_than_hs_diploma, percent_unemployed)) +
  geom_point(size = 0.1) +
  geom_smooth(se = F)
```

There is a positive relationship between percent not attaining a high school diploma and unemployment rate, which means the lower percent not attaining a high school diploma would lead to a smaller unemployment rate. 


